|

### 2025-01-24 output/seminar-slideshow.qmd
Changes example to exaggerate difference in length
The new example of the coordinate transformation takes a point with very small coordinates and makes its transformed coordinates much bigger

::::: columns
::: column
```{r oblique-rotation-axis-1}
LIM_INF <- -0.5
LIM_SUP <-  2.5

axis_lims <- c(LIM_INF, LIM_SUP)

point <- tibble(F1 = 2.4, F2 = .1)

@@

point |>
  ggplot(mapping = aes(F1, F2))            +
  geom_segment(
    data    = point_spikes,
    mapping = aes(F1_start, F2_start, xend = F1_end, yend = F2_end),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
  )                                        +
  geom_point(size = I(4))                  +
  scale_x_continuous(
    limits = axis_lims,
    breaks = 0,
    labels = NULL,
    name   = NULL
  )                                        +
  scale_y_continuous(
    limits = axis_lims,
    breaks = 0,
    labels = NULL,
    name   = NULL
  )                                        +
  coord_fixed(expand = FALSE, clip = "on") +
  theme(
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    panel.grid.major   = element_line(
      color     = "black",
      linewidth = GRID_WIDTH
    )
  )
```
:::

@@

BASIS_VEC_1 <- c(1, 0)
BASIS_VEC_2 <- c(12, 1)
BASIS_VEC_2 <- BASIS_VEC_2 / sqrt(sum(BASIS_VEC_2^2))

axis_lims  <- c(LIM_INF, LIM_SUP)
axis_slope <- BASIS_VEC_2[2] / BASIS_VEC_2[1]
transf_matrix <- cbind(BASIS_VEC_1, BASIS_VEC_2) |> unname()

@@

point |>
  ggplot(mapping = aes(F1, F2)) +
  geom_abline(slope = axis_slope) +
  geom_segment(
    data    = point_spikes,
    mapping = aes(F1_start, F2_start, xend = F1_end, yend = F2_end),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
    color = SEC_COLOR
  ) +
  geom_segment(
    data    = point_spikes_transf_ob,
    mapping = aes(start_F1, start_F2, xend = end_F1, yend = end_F2),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43'
  ) +
  geom_point(size = I(4)) +
  scale_x_continuous(
    limits = axis_lims,
    breaks = 0,
    labels = NULL,
    name   = NULL
  ) +
  scale_y_continuous(
    limits = axis_lims,
    breaks = 0,
    labels = NULL,
    name   = NULL
  ) +
  coord_fixed(expand = FALSE, clip = "on") +
  theme(
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    # panel.grid.major   = element_line(linewidth = GRID_WIDTH),
    panel.grid.major.x = element_line(
      linewidth = GRID_WIDTH,
      color = SEC_COLOR
    ),
    panel.grid.major.y = element_line(linewidth = GRID_WIDTH, color = "black")
  )
```
:::

@@

```{r oblique-rotation-rect-coords}
point_transf |>
  ggplot(mapping = aes(F1, F2))            +
  geom_segment(
    data    = point_spikes_transf,
    mapping = aes(F1_start, F2_start, xend = F1_end, yend = F2_end),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
  )                                        +
  geom_point(size = I(4))                  +
  scale_x_continuous(
    limits = axis_lims,
    breaks = 0,
    labels = NULL,
    name   = NULL
  )                                        +
  scale_y_continuous(
    limits = axis_lims,
    breaks = 0,
    labels = NULL,
    name   = NULL
  )                                        +
  coord_fixed(expand = FALSE, clip = "on") +
  theme(
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    panel.grid.major   = element_line(
      color     = "black",
      linewidth = GRID_WIDTH
    )
  )
```
:::
:::::

>>>>

::::: columns
::: column
```{r oblique-rotation-axis-1}
LIM_INF_X <- -2.7
LIM_INF_Y <- -0.5
LIM_SUP   <-  2.7

axis_lims_x <- c(LIM_INF_X, LIM_SUP)
axis_lims_y <- c(LIM_INF_Y, LIM_SUP)

point <- tibble(F1 = .1, F2 = .3)

@@

point |>
  ggplot(mapping = aes(F1, F2))            +
  geom_segment(
    data    = point_spikes,
    mapping = aes(F1_start, F2_start, xend = F1_end, yend = F2_end),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
  )                                        +
  geom_point(size = I(4))                  +
  scale_x_continuous(
    limits = axis_lims_x,
    breaks = 0,
    labels = NULL,
    name   = NULL
  )                                        +
  scale_y_continuous(
    limits = axis_lims_y,
    breaks = 0,
    labels = NULL,
    name   = NULL
  )                                        +
  coord_fixed(expand = FALSE, clip = "on") +
  theme(
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    panel.grid.major   = element_line(
      color     = "black",
      linewidth = GRID_WIDTH
    )
  )
```
:::

@@

BASIS_VEC_1 <- c(1, 0)
BASIS_VEC_2 <- c(-8, 1)
BASIS_VEC_2 <- BASIS_VEC_2 / sqrt(sum(BASIS_VEC_2^2))

axis_slope <- BASIS_VEC_2[2] / BASIS_VEC_2[1]
transf_matrix <- cbind(BASIS_VEC_1, BASIS_VEC_2) |> unname()

@@

point |>
  ggplot(mapping = aes(F1, F2)) +
  geom_abline(slope = axis_slope, linewidth = GRID_WIDTH) +
  geom_segment(
    data    = point_spikes,
    mapping = aes(F1_start, F2_start, xend = F1_end, yend = F2_end),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
    color = SEC_COLOR
  ) +
  geom_segment(
    data    = point_spikes_transf_ob,
    mapping = aes(start_F1, start_F2, xend = end_F1, yend = end_F2),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43'
  ) +
  geom_point(size = I(4)) +
  scale_x_continuous(
    limits = axis_lims_x,
    breaks = 0,
    labels = NULL,
    name   = NULL
  ) +
  scale_y_continuous(
    limits = axis_lims_y,
    breaks = 0,
    labels = NULL,
    name   = NULL
  ) +
  coord_fixed(expand = FALSE, clip = "on") +
  theme(
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    # panel.grid.major   = element_line(linewidth = GRID_WIDTH),
    panel.grid.major.x = element_line(
      linewidth = GRID_WIDTH,
      color = SEC_COLOR
    ),
    panel.grid.major.y = element_line(linewidth = GRID_WIDTH, color = "black")
  )
```
:::

@@

```{r oblique-rotation-rect-coords}
point_transf |>
  ggplot(mapping = aes(F1, F2))            +
  geom_segment(
    data    = point_spikes_transf,
    mapping = aes(F1_start, F2_start, xend = F1_end, yend = F2_end),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
  )                                        +
  geom_point(size = I(4))                  +
  scale_x_continuous(
    limits = axis_lims_x,
    breaks = 0,
    labels = NULL,
    name   = NULL
  )                                        +
  scale_y_continuous(
    limits = axis_lims_y,
    breaks = 0,
    labels = NULL,
    name   = NULL
  )                                        +
  coord_fixed(expand = FALSE, clip = "on") +
  theme(
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    panel.grid.major   = element_line(
      color     = "black",
      linewidth = GRID_WIDTH
    )
  )
```
:::
:::::
